Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-12-09 results.tex
updating figure 1 and 3

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{feed_assays}
        \caption{Feed Assays}
        \label{sfig:feed_assay}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{product_assays}
        \caption{Product Assays}
        \label{sfig:product_assay}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{tails_assays}
        \caption{Tails Assays}
        \label{sfig:tails_assay}
    \end{subfigure}
    \caption{Feed (\subref{sfig:feed_assay}), product
        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
        in $w\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
        blue), per model (A/B/C) and without/with tails recycling (NR/R). The
        black dashed line represents the $90 w\%$ enrichment threshold.}
    \label{fig:assays}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{feed_assays}
        \caption{Feed Assays}
        \label{sfig:feed_assay}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{product_assays}
        \caption{Product Assays}
        \label{sfig:product_assay}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{tails_assays}
        \caption{Tails Assays}
        \label{sfig:tails_assay}
    \end{subfigure}
    \caption{Feed (\subref{sfig:feed_assay}), product
        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
        in $w\%$ of $^{235}$U, per cascade level from 0 to 4 (purple, red, green,
        orange, blue), per model (A/B/C) and without/with tails recycling (NR/R).
        The black dashed line represents the $90 w\%$ enrichment threshold.}
    \label{fig:assays}
\end{figure}
